Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-12 paper/paper.tex
adding hermes bug in discussion

%\Mar{@Gustavo,@Breno, can you please make this par a bit stronger
%  (more coherent/compelling) as to justify the selection of these two
%  techniques?}
%\Breno{Changed the paragraph a bit to include the reuse argument.}
We selected these two techniques because they can take advantage
of existing test suites and reuse them --- in a semi-automated way
as we propose here --- to enhance the coverage of the engine under testing.
%These techniques demand different effort from developers.
Cross-engine differential testing is semi-automated as
developers need to decide if alarms are manifestations of real
bugs. Test transplantation is fully automated, but it can only reveal
bugs that the original tests could reveal. This study measures the
ability of these techniques in finding bugs and the human cost
associated with each technique.

@@

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~The most important contribution of this work is
empirical: we provide a comprehensive study analyzing the
effectiveness of test transplantation and differential testing in
revealing functional bugs in popular \javascript\ engines.  Additional
contributions include: 1)~A number of bugs found and fixed.  We
reported a total of \totalBugsReported bugs.  Of these,
\totalBugsConfirmed bugs were confirmed and \totalBugsFixed bugs were
fixed.  2)~An infrastructure for performing test transplantation and
differential testing. The soruce code produced and the generated data sets of tests
and bugs are publicly available online at the following link:

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:test-suites}Number of test files. Dashed
    rectangle under column ``type-in-all'' shows the tests used for
    test transplantation whereas the rectangle under column
    ``no-fail-in-all''---a subset of the ``type-in-all'' tests---shows
    the tests used in cross-engine differential
    testing.}
  \setlength{\tabcolsep}{2pt}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{4}{c}{\# JS files} \\
    \cline{3-6}
                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
    \midrule
    Test262 & \cite{ecma262-conformance-suite} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
    \midrule
    \jsc & \cite{jsc2018repo} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
    \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
    \veight{} & \cite{v82018repo} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
    %\chakra & \cite{chakra2018repo}\\
    %\hermes & \cite{hermes2020repo} & \hermesOriginal{} & \hermesPassInPar{} & \hermesCompileAll{} & \hermesNoFailAll{} \\
    \midrule
    Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\
    \jerry{} & \cite{jerryscript2018repo} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
    JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
    %\midrule
    %GitHub Projects & - & 494,394 & - & - & - \\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule
  \end{tabular}
\end{table}

@@

We used two black-box mutational fuzzers in this
study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
fuzzers require no instrumentation and domain-knowledge. They mutate
existing inputs randomly. The strength of the approach is
limited by the quality of the test suite and the supported mutation
operators, which are typically simple. We chose these specific fuzzers
because, conceptually, one complements the other. \quickfuzz\ creates
mutations like \radamsa. However, in contrast to \radamsa, \quickfuzz\ is aware
of the \js\ syntax; it is able to replace sub-trees of the syntax
tree~\cite{grieco2016quickfuzz} with trees created anew. Notwithstanding,
since \radamsa performs simpler syntactic source code modifications,
it also produces a higher number of valid inputs (when compared with,
for instance, AFL).

@@

\Mar{--------------- estou aqui}

@@

\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:bugs}.} We
reported the code snippet below to the \smonkey\ development team as a
bug, the bug was confirmed in a few hours.

\begin{figure}[h!]
  \vspace{-0.5ex}
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function,
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
    "use strict"
    010
  \end{lstlisting}
  \normalsize
  %% \caption{Warning captured as \hi{} priority.}
  %% \label{fig:hi-priority}
  \vspace{-1ex}
\end{figure}

@@

>>>>

\Mar{@Gustavo,@Breno, can you please make this par a bit stronger
  (more coherent/compelling) as to justify the selection of these two
  techniques?}
\Breno{Changed the paragraph a bit to include the reuse argument.}
We selected these two techniques because they can take advantage
of existing test suites and reuse them --- in a semi-automated way
as we propose here --- to enhance the coverage of the engine under testing.
%These techniques demand different effort from developers.
Cross-engine differential testing is semi-automated as
developers need to decide if alarms are manifestations of real
bugs. Test transplantation is fully automated, but it can only reveal
bugs that the original tests could reveal. This study measures the
ability of these techniques in finding bugs and the human cost
associated with each technique.

@@

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~The most important contribution of this work is
empirical: we provide a comprehensive study analyzing the
effectiveness of test transplantation and differential testing in
revealing functional bugs in popular \javascript\ engines.  Additional
contributions include: 1)~A number of bugs found and fixed.  We
reported a total of \totalBugsReported bugs.  Of these,
\totalBugsConfirmed bugs were confirmed and \totalBugsFixed bugs were
fixed.  2)~An infrastructure called \entente for performing test transplantation and
differential testing.  Both \entente code and the data sets of tests
and bugs are publicly available online at the following link:

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:test-suites}Number of test files. Dashed
    rectangle under column ``type-in-all'' shows the tests used for
    test transplantation whereas the rectangle under column
    ``no-fail-in-all''---a subset of the ``type-in-all'' tests---shows
    the tests used in cross-engine differential
    testing.\Gustavo{Terminar essa tabela}}
  \setlength{\tabcolsep}{2pt}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{4}{c}{\# JS files} \\
    \cline{3-6}
                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
    \midrule
    Test262 & \cite{ecma262-conformance-suite} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
    \midrule
    \jsc & \cite{jsc2018repo} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
    \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
    \veight{} & \cite{v82018repo} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
    %\chakra & \cite{chakra2018repo}\\
    \hermes & \cite{hermes2020repo} & \hermesOriginal{} & \hermesPassInPar{} & \hermesCompileAll{} & \hermesNoFailAll{} \\
    \midrule
    Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\
    \jerry{} & \cite{jerryscript2018repo} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
    JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
    \midrule
    GitHub Projects & - & 494,394 & - & - & - \\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule
  \end{tabular}
\end{table}

@@

We used two black-box mutational fuzzers in this
study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
fuzzers require no instrumentation and domain-knowledge. They mutate
existing inputs randomly. The strength of the approach is
limited by the quality of the test suite and the supported mutation
operators, which are typically simple. We chose these specific fuzzers
because, conceptually, one complements the other. \quickfuzz\ creates
mutations like \radamsa. However, in contrast to \radamsa, \quickfuzz\ is aware
of the \js\ syntax; it is able to replace sub-trees of the syntax
tree~\cite{grieco2016quickfuzz} with trees created anew.

@@

@@

\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:test-transplantation-bugs}.} We
reported the code snippet below to the \smonkey\ development team as a
bug, the bug was confirmed in a few hours.

\begin{figure}[h!]
  \vspace{-0.5ex}
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function,
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
    "use strict"
    010
  \end{lstlisting}
  \normalsize
  \vspace{-1ex}
\end{figure}

@@

\vspace{1ex}\noindent\textbf{Issue \#24, Table~\ref{tab:bugs}.} The snippet 
above represents a bug confirmed in \hermes\ engine with 
differential testing using radamsa on a repository mined from GitHub.

\begin{figure}[h!]
  \vspace{-0.5ex}
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function,
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
    b+/v/a
  \end{lstlisting}
  \normalsize
  \vspace{-1ex}
\end{figure}

The original test case contains a string concatenation. 
This is a case of validation of RegExp flags because the fuzzer mutated
the file with a regular expression "/v/" between the variables.
The plus operator in this case is set as a flag of the RegExp "+/v/",
but in this case the plus operator is not valid as a flag. The behavior expected
is throws an early SyntaxError due to a invalid regular expression flag,
but \hermes seems not threat the early validation of the regexp flags as 
commented by a team developer.
